### 2020-04-23 writeup/setup.tex
wip

Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
We study a high-dimensional linear regression setting under covariate and model shifts.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
These are achieved through tight generalization bounds established in the high-dimensional regression setting.

>>>>

Multi-task learning that is applied on heterogeneous data can often result in suboptimal models (or negative transfer in more technical terms).
In a previous work \cite{WZR20}, we identified three factors that help determine when multi-task learning works, and when it doesn't.
In this work, we zoom in to the task covariance part of \cite{WZR20} to further understand when multi-task learning works for heterogeneous data.
We study a high-dimensional linear regression setting where the target task data size is limited.
We formulate the heterogeneity between different task data under covariate and model shifts \cite{PY09,K18}.
By using random matrix theory, we can explain several phenomena that are not explained by the techniques of \cite{WZR20}.
\todo{list those here}
These are achieved through tight generalization bounds established in the high-dimensional regression setting using random matrix theory.
